From Poplink

### 2018-03-04 CreData/fromPoplink.Rmd
continue
considerations

---
title: "From Poplink"
author: "Göran Broström"
date: "28 February 2018"
output:
  pdf_document: default
  html_document: default
---

@@

```{r propagate}
##if (file.exists("adult.rda")){
  ##load("adult.rda")
if (TRUE){
source("R/fixCovar2.R")  
    adult$hisclass40 <- with(adult, fixCovar2(id, hisclass, enter, exit, 40, 20))
    adult$hisclass40[is.na(adult$hisclass40)] <- 5
    adult$hisclass40 <- factor(adult$hisclass40, labels = c("elite", "middle", "worker", "farmer", "none"))
    adult$hisclass65 <- with(adult, fixCovar2(id, hisclass, enter, exit, 65, 45))
    adult$hisclass65[is.na(adult$hisclass65)] <- 5
    adult$hisclass65 <- factor(adult$hisclass65, labels = c("elite", "middle", "worker", "farmer", "none"))

@@

}else{
  adult <- adult[order(adult$id, adult$enter), ]
  adult <- group_by(adult, id) %>% fill_("hisclass")
  adult$hisclass[is.na(adult$hisclass)] <- 4
  adult$hisclass <- factor(adult$hisclass, labels = c("elite", "middle", "worker", "NA"))
  ##
  adult <- group_by(adult, id) %>%  fill_("civst")
  adult$civst[is.na(adult$civst)] <- "unmarried"
  save(adult, file = "adult.rda")
}
```

>>>>

---
title: "From Poplink"
author: "Göran Broström"
date: "4 March, 2018"
output:
  html_document: default
  pdf_document: default
---

@@

```{r propagate}
##if (file.exists("adult.rda")){
  ##load("adult.rda")
if (TRUE){
    adult <- adult[order(adult$id, adult$enter), ]
    adult <- group_by(adult, id) %>% fill_("hisclass")
    source("R/pus")
    source("R/fixCovar2.R")  
    adult$hisclass40 <- with(adult, fixCovar2(id, hisclass, enter, exit, 40, 20))
    adult$hisclass40[is.na(adult$hisclass40)] <- 5
    adult$hisclass40 <- factor(adult$hisclass40, labels = c("elite", "middle", "worker", "farmer", "none"))
    adult$hisclass65 <- with(adult, fixCovar2(id, hisclass, enter, exit, 65, 45))
    adult$hisclass65[is.na(adult$hisclass65)] <- 5
    adult$hisclass65 <- factor(adult$hisclass65, labels = c("elite", "middle", "worker", "farmer", "none"))

@@

}else{
  adult$hisclass[is.na(adult$hisclass)] <- 4
  adult$hisclass <- factor(adult$hisclass, labels = c("elite", "middle", "worker", "NA"))
  ##
  adult <- group_by(adult, id) %>%  fill_("civst")
  adult$civst[is.na(adult$civst)] <- "unmarried"
  save(adult, file = "adult.rda")
}
```
